Supporting Information

### 2016-08-13 portfolio/text/ms.Rmd
Add text skeleton
Integrate output values

---
title: Title here
author: |
  | Authors here
date: ""
geometry: margin=1.1in
fontfamily: libertine
fontsize: 12pt
output: pdf_document
---

@@

@@

@@

# References

>>>>

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
```

```{r get-dat, cache=FALSE}
load("../data-generated/output-values.rda")
```

@@

[@kasperski2013]
[@simpson1949]
[@sethi2012b]
[@sethi2014]

@@

[@standevelopmentteam2015]

@@

\bibliographystyle{apalike}
\bibliography{refs}

### 2016-08-13 portfolio/text/supp.Rnw
Integrate output values

@@

 % mm <- model.matrix(log(revenue) ~ -1 + b1(spec_change) + b2(spec_change) +
      % days_change + b1(spec_change):days_change + b2(spec_change):days_change,

@@

We fit our models in Stan version 2.11.1. \ldots

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Caption here}
\label{fig:ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Caption here}
\label{fig:ts}
\end{center}
\end{figure}

>>>>

<<set-knitr-options, cache=FALSE, echo=FALSE>>=
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
@

<<get-values, cache=FALSE>>=
load("../data-generated/output-values.rda")
@

@@

Rows of data: \Sexpr{nrows}.
Number of permit holders: \Sexpr{npholders}.
Range of years: \Sexpr{range_yrs}.
Number of strategies: \Sexpr{nstr}

\citep{gelman2014}

@@

We fit our models in Stan version 2.11.1. \ldots
\citep{hoffman2014, standevelopmentteam2015a, carpenter2015a, standevelopmentteam2015}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Caption here}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Caption here}
\label{fig:re}
\end{center}
\end{figure}
